---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = NA,
  echo = FALSE,
  eval = TRUE
)
suppressPackageStartupMessages({
    library(tidyverse)
    library(remotes)
})
```


# trans_trends

[![DOI](https://zenodo.org/badge/227422889.svg)](https://zenodo.org/badge/latestdoi/227422889)


Code and data for the paper, "Heterogeneous responses of tundra 
arthropods to spatiotemporal variation in resource subsidies."
The R package that fits the models can be found at 
<https://github.com/lucasnell/trans_trends_pkg>.

This repository was created and is maintained by
[Lucas A. Nell](https://github.com/lucasnell).



# Organization

These are the main top-level files/folders:

```{bash, echo = TRUE, eval = FALSE}
.
├── .Rprofile
├── README.Rmd
├── README.md
├── renv.lock
├── trans_trends.Rproj
├── data
├── figures
├── rds_files
├── renv
└── scripts
```

The following files/folders should be present:

- `.Rprofile`: small file that contains R code that is run when R is started.
  Used for `renv` package.
- `README.md` and `README.Rmd`: this file and the file that generates it,
  respectively (only `README.Rmd` should be edited)
- `renv.lock`: JSON file containg info about all the packages (and their 
  versions) to install to replicate our R environment using the `renv` package
- `trans_trends.Rproj`: file saving this RStudio Project's preferences
- `data`: Folder containing all datasets associated with this paper.
- `figures`: Folder containing figures created from this paper.
  Note that this folder should be empty and is populated by running the
  R scripts.
- `rds_files`: Folder containing RDS files created for model fits and 
  cleaned data.
  Note that this folder should be empty and is populated by running the
  R scripts.
- `renv`: Largely empty folder containing the R package library if using
  the `renv` package to replicate our R environment
- `scripts`: Folder containing R scripts for data cleanup, model fitting, and 
  creating figures / tables.

Note that all folders except `renv` have their own `README.md` files that 
should be referenced for specific files.



# Replicating the R environment

I used `r R.version.string` (platform: `r R.version[["platform"]]`) for all my scripts.

This project uses the `renv` package, so if you want to use this, you must
first install it:

```{r, echo = TRUE, eval = FALSE}
install.packages("renv")
```

Then to install all the packages I used for these analyses, you can simply run
the following while having this project's main directory as your working
directory:

```{r, echo = TRUE, eval = FALSE}
renv::restore()
```


If you'd rather avoid `renv`, then you can install all the packages 
(in the versions I used) this way:

```{r, echo = TRUE, eval = FALSE}
if (!requireNamespace("jsonlite", quietly = TRUE)) install.package("jsonlite")
pkg_list <- jsonlite::read_json("renv.lock")[["Packages"]]
pkg_vers <- lapply(pkg_list, \(x) paste0(x[["Package"]], "@", x[["Version"]]))
pkg_vers[["TransTrendsPkg"]] <- NULL  # bc we're getting this one from github

# Most packages from CRAN:
install.packages(do.call(c, pkg_vers))

# Now TransTrendsPkg from GitHub:
remotes::install_github(paste0("lucasnell/trans_trends_pkg@",
                               pkg_list[["TransTrendsPkg"]][["RemoteSha"]]))
```

