---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = NA,
  echo = FALSE,
  eval = TRUE
)
suppressPackageStartupMessages({
    library(tidyverse)
    library(remotes)
})
```


# trans_trends

[![DOI](https://zenodo.org/badge/227422889.svg)](https://zenodo.org/badge/latestdoi/227422889)


Code and data for the paper, "Heterogeneous responses of tundra 
arthropods to spatiotemporal variation in resource subsidies."
The R package that fits the models can be found at 
<https://github.com/lucasnell/trans_trends_pkg>.

This repository was created and is maintained by
[Lucas A. Nell](https://github.com/lucasnell).



# Organization

These are the top-level files/folders:

```{bash, echo = TRUE, eval = FALSE}
.
├── README.md
├── trans_trends.Rproj
├── data
├── figures
├── rds_files
└── scripts
```

The following files/folders should be present:

- `README.md`: this file
- `trans_trends.Rproj`: file saving this RStudio Project's preferences
- `data`: Folder containing all datasets associated with this paper.
- `figures`: Folder containing figures created from this paper.
  Note that this folder should be empty and is populated by running the
  R scripts.
- `rds_files`: Folder containing RDS files created for model fits and 
  cleaned data.
  Note that this folder should be empty and is populated by running the
  R scripts.
- `scripts`: Folder containing R scripts for data cleanup, model fitting, and 
  creating figures / tables.

Note that all folders have their own `README.md` files that should be
referenced for specific files.



# Replicating the R environment

I used `r R.version.string` (platform: `r R.version[["platform"]]`) for all my scripts.

This project uses the `renv` package, so if you want to use this, you must
first install it:

```{r, echo = TRUE, eval = FALSE}
install.packages("renv")
```

Then to install all the packages I used for these analyses, you can simply run
the following while having this project's main directory as your working
directory:

```{r, echo = TRUE, eval = FALSE}
renv::restore()
```


If you'd rather avoid `renv`, then you can install all the packages 
(in the versions I used) this way:

```{r, results = "asis"}
loaded_pkgs  <- c("ggspatial", "patchwork", "sf", "tidyverse", "viridisLite") |> 
    map_chr(\(p) sprintf("%s@%s", p, packageVersion(p)))
# packages required for `TransTrendsPkg`:
tt_pkgs <- dev_package_deps("../trans_trends_pkg/") |> 
    as_tibble() |> 
    select("package","installed") |> 
    pmap_chr(paste, sep = "@")
all_pkgs <- c(loaded_pkgs, tt_pkgs) |> unique() |> sort()
# Turn into two columns:
pkg_2cols <- map_chr(seq(1:ceiling(length(all_pkgs)/2)),
                     \(i) {
                         j <- (i-1)*2 + 1
                         k <- min(j+1, length(all_pkgs))
                         sp <- ifelse(i == 1, "", "          ")
                         paste0(sp, paste(sprintf('"%s"', all_pkgs[j:k]), 
                                          collapse = ", "))
                     }) |> 
    paste(collapse = ",\n") |> 
    sprintf(fmt = "pkgs <- c(%s)\n")
cat("```r\n")
cat(pkg_2cols)
cat('install.packages(pkgs)\n')
cat('install.packages("remotes")\n')
cat(sprintf('remotes::install_github("lucasnell/trans_trends_pkg@%s")\n',
            packageVersion("TransTrendsPkg")))
cat("```\n")
```


Note that these only install the proper versions of the packages I manually 
installed (or were dependencies of `TransTrendsPkg`),
so dependencies might vary from what I used.


Similarly, but without version numbers at all:

```{r, results = "asis"}
pkg_2cols <- map_chr(seq(1:ceiling(length(all_pkgs)/4)),
        \(i) {
            j <- (i-1)*4 + 1
            k <- min(j+3, length(all_pkgs))
            sp <- ifelse(i == 1, "", "          ")
            p <- str_split(all_pkgs[j:k],"@") |> 
                map_chr(\(x) x[1])
            paste0(sp, paste(sprintf('"%s"', p), 
                             collapse = ", "))
        }) |> 
    paste(collapse = ",\n") |> 
    sprintf(fmt = "pkgs <- c(%s)\n")
cat("```r\n")
cat(pkg_2cols)
cat('install.packages(pkgs)\n')
cat('install.packages("remotes")\n')
cat('remotes::install_github("lucasnell/trans_trends_pkg")\n')
cat("```\n")
```
